%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {HPC Software Engineer} % Job title
    {Contractor at TotalEnergies, working for Capgemini} % Organisation
    {Pau, France} % Location
    {Sept 2018 - Sep 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and enhanced commercial reservoir simulation software with complex physics and usability features.}
        \item {Worked across Linux and Windows environments using \textbf{C++}, \textbf{Python}, MPI, and multithreading.}
        \item {Applied software engineering best practices, including efficient algorithms, design patterns, and comprehensive unit \& regression testing.}
        \item {Utilized \textbf{Azure DevOps} for issue tracking and CI/CD pipelines, and Git for source code version control.}
        \item {Collaborated with cross-functional teams from 3 companies.}
        \item {Followed Agile methodologies to ensure iterative development and continuous improvement.}
        \item {\textbf{Technical Skills:} C++, Python, MPI, multithreading, Linux/Windows, Git, Azure DevOps, CI/CD, software engineering best practices.}
        \item {\textbf{Soft Skills:} Cross-functional collaboration, Agile teamwork, communication, time management.}
      \end{cvitems}
    }

  \cventry
    {Cofonder} % Job title
    {Geophysics Anywhere} % Organisation
    {Bogota, Colombia} % Location
    {2016 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founded a startup focused on geophysical software for seismic data processing.}
        \item {Designed and developed a SaaS platform for intuitive seismic data analysis.}
        \item {Provided technical support to customers and managed client relationships.}
        \item {Led marketing efforts including Google Ads campaigns and participation in industry conferences.}
        \item {Secured seed funding from Fondo Emprender to launch and grow the company.}
        \item {\textbf{Technical Skills:} Python, Node.js, Linux tools, Git, SaaS development, Google Ads.}
        \item {\textbf{Soft Skills:} Client relationship, strategic planning, marketing, teamwork.}
      \end{cvitems}
    }

    \cventry
      {Research Engineer} % Job title
      {Corporación Geológica Ares} % Organisation
      {Bogota, Colombia} % Location
      {2015 - 2017} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Developed a 5D seismic interpolation method based on Projections Onto Convex Sets (POCS) for improved data reconstruction.}
          \item {Implemented core algorithms using Fortran90 for high-performance computing.}
          \item {Built software tools to automate seismic acquisition data processing workflows.}
          \item {Utilized Seismic Unix and Madagascar for seismic data preprocessing and visualization.}
          \item {Created Bash scripts to process tasks in a Linux environment.}
          \item {\textbf{Technical Skills:} Fortran90, Python, C++, seismic processing (Seismic Unix, Madagascar), Bash scripting, Linux.}
          \item {\textbf{Soft Skills:} Research, workflow automation, scientific collaboration.}
        \end{cvitems}
      }

   \cventry
      {Assistant professor} % Job title
      {Universidad Antonio Nariño} % Organisation
      {Bogota, Colombia} % Location
      {2014} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Taught undergraduate courses in Logic, Simulation, and Bio-mathematics.}
          \item {Conducted research on complex fluid flow simulation at the pore scale, with applications in oil recovery.}
          \item {\textbf{Technical Skills:} Simulation techniques, fluid dynamics modeling.}
          \item {\textbf{Soft Skills:} Academic research, teaching, collaboration.}
        \end{cvitems}
      }

   \cventry
      {Part time assistant professor} % Job title
      {Universidad Autónoma de Bucaramanga} % Organisation
      {Bucaramanga, Colombia} % Location
      {2013} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Taught undergraduate course in Discrete Mathematics.}
          \item {Contributed to academic instruction and supported student learning in foundational computer science topics.}
          \item {\textbf{Technical Skills:} Discrete mathematics instruction.}
          \item {\textbf{Soft Skills:} Academic support, teaching, collaboration}
        \end{cvitems}
      }

  \cventry
    {Ph.D. in Applied Mechanics} % Job title
    {MFEE Department (EDF), in collaboration with TREFLE Laboratory (Bordeaux I)} % Organisation
    {Bordeaux, France} % Location
    {2009 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a second-order penalty method for fluid dynamics simulations.}
        \item {Implemented parallel algorithms using Fortran, C++, and MPI.}
        \item {Conducted numerical simulations using finite volume methods on both structured and unstructured meshes.}
        \item {Integrated the model into: Thetis: Academic CFD software (structured mesh). Code\_Saturne®: Industrial CFD software (unstructured mesh).}
        \item {Utilized Tecplot, Paraview, and Ensight for post-processing and results visualization.}
        \item {Automated workflows and data handling using Bash scripting.}
        \item {\textbf{Technical Skills:} Fortran, C++, MPI, CFD (Code\_Saturne®, Thetis), finite volume methods, Tecplot, Paraview, Ensight, Bash.}
        \item {\textbf{Soft Skills:} Academic research, problem-solving, collaboration, technical writing, time management.}
      \end{cvitems}
    }

\end{cventries}
